---
title: "Uncertainty Grammar of Graphics"
author: "Xiaoying Pu"
date: "9/29/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(riskyr)
library(rv2)
library(proto)
```

# Data representation

## riskyr

Icon array 

```{r}
plot_icons(prev = .01, sens = .80, spec = NA, fart = .096, N = 1000, 
           icon.types = c(21, 21, 22, 22),
           title.lbl = "Mammography screening")
```

Generating frequencies from probabilities

```{r}
f1 <- comp_freq_prob(prev = .1, sens = .70, spec =   NA, fart = .090, N = 1000)
length(f1)
```

```{r}
plot_mosaic(prev = .1, sens = .70, spec =   NA, fart = .090, N = 1000,
            title.lbl = "Mammography screening")
```

## rv2

- Random variable
- simulate from prob. distributions

```{r}
dice <- rv(1:6)
dice
plot(dice)
P(dice <= 3)
E(dice) 
rsim(dice, 100) # simulate random numbers from rv
```


# Example dataset

For this made-up dataset: `prev = .1, sens = .70, spec =   NA, fart = .090, N = 1000`, create a dataframe instead of having four function arguments

- Pro: an handle more than two variables, not limited to binary variables, like tidy data?
- Con: inefficient?








