---
title: "Uncertainty Grammar of Graphics"
author: "Xiaoying Pu"
date: "9/29/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(riskyr)
library(rv2)
library(tidyverse)
library(ggplot2)
```

# Data representation

## riskyr

Icon array 

```{r}
plot_icons(prev = .1, sens = .70, spec =   NA, fart = .090, N = 100,
           icon.types = c(21, 21, 22, 22),
           title.lbl = "Mammography screening")
```

Generating frequencies from probabilities

```{r}
f1 <- comp_freq_prob(prev = .1, sens = .70, spec =   NA, fart = .090, N = 100)
length(f1)
f1
```

```{r}
plot_mosaic(prev = .1, sens = .70, spec =   NA, fart = .090, N = 100,
            title.lbl = "Mammography screening")
```

## rv2

- Random variable
- simulate from prob. distributions

```{r}
dice <- rv(1:6)
dice
plot(dice)
P(dice <= 3)
E(dice) 
rsim(dice, 100) # simulate random numbers from rv
```


# Example dataset

For this made-up dataset: `prev = .1, sens = .70, spec =   NA, fart = .090, N = 100`, create a dataframe instead of having four function arguments

- Pro: an handle more than two variables, not limited to binary variables, like tidy data?
- Con: inefficient?

Spec: 

- Each row is one sample
- Each column is a random variable
- Each cell is a number (or factor)???


## As dataframe

Build the dataframe:


```{r}
df <- data.frame(
  cancer = c(rep(1, 10),  rep(0, 90)), 
  test = c(rep(1, 7), rep(0, 3), rep(1, 8), rep(0, 82)))
```

## As random variable


TODO: How to express conditional probabilities?

```{r}
cancer <- rv(x = c(1, 0), probs = c(0.1, 0.9))
test <- rv(x = c(1,0), probs = c(0.15, 0.85))
```


# ggplot tutorial

https://cran.r-project.org/web/packages/ggplot2/vignettes/extending-ggplot2.html
https://github.com/tidyverse/ggplot2/blob/master/R/stat-count.r
https://www.rdocumentation.org/packages/ggplot2/versions/3.0.0/topics/ggplot2-ggproto


## ggproto

### Stat for P(B|A)

```{r}
StatConditionalProb <- ggproto("StatConditionalProb", Stat,
  compute_group = function(data, scales, width = NULL ){
    # data[chull(data$x, data$y), , drop = FALSE]
    # y_given_x <- data[data$x == 1, ]$y
    # y <- data.frame(table(y_given_x))
    # print(y)
    # y
    
    x <- data[data$x == 1, ]$y
    weight <- data$weight %||% rep(1, length(x))
    width <- width %||% (resolution(x) * 0.9)

    count <- as.numeric(tapply(weight, x, sum, na.rm = TRUE))
    count[is.na(count)] <- 0
    data.frame(
      count = count,
      prop = count / sum(abs(count)),
      x = sort(unique(x)),
      width = width
    )
  },
  
  required_aes = c("x", "y")
)
```

### Layer for P(B|A)

```{r}
stat_conditional_prob <- function(mapping = NULL, data = NULL,
                                  geom = "bar", position = "stack",
                                  ...,
                                  width = NULL,
                                  na.rm = FALSE,
                                  show.legend = NA,
                                  inherit.aes = TRUE) {
  
  params <- list(
    na.rm = na.rm,
    width = width,
    ...
  )
  layer(
    data = data,
    mapping = mapping,
    stat = StatConditionalProb,
    geom = geom,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = params
  )
}
```

### Plot

Using fake stat_count

```{r}
stat_c <- function(mapping = NULL, data = NULL,
                       geom = "bar", position = "stack",
                       ...,
                       width = NULL,
                       na.rm = FALSE,
                       show.legend = NA,
                       inherit.aes = TRUE) {

  params <- list(
    na.rm = na.rm,
    width = width,
    ...
  )
  if (!is.null(params$y)) {
    stop("stat_count() must not be used with a y aesthetic.", call. = FALSE)
  }

  layer(
    data = data,
    mapping = mapping,
    stat = StatCount,
    geom = geom,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = params
  )
}


StatCount <- ggproto("StatCount", Stat,
  required_aes = "x",
  default_aes = aes(y = stat(count), weight = 1),

  setup_params = function(data, params) {
    if (!is.null(data$y)) {
      stop("stat_count() must not be used with a y aesthetic.", call. = FALSE)
    }
    params
  },

  compute_group = function(self, data, scales, width = NULL) {
    positive <- df[df$cancer == 1, ]$test
    negative <- df[df$cancer == 0, ]$test + 2
    x <- c(positive, negative)
    weight <- data$weight %||% rep(1, length(x))
    width <- width %||% (resolution(x) * 0.9)

    count <- as.numeric(tapply(weight, x, sum, na.rm = TRUE))
    count[is.na(count)] <- 0

    data.frame(
      count = count,
      prop = count / sum(abs(count)),
      x = sort(unique(x)),
      width = width
    )
  }
)
```


```{r}
ggplot(df, aes(x= cancer)) + 
  stat_c()
```

