---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: inline
---

editor_options:
  chunk_output_type: console
  
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
library(gridExtra)
library(productplots)
```

_This document generates several figures used in the pgog paper_

# Override default themes

```{r}
custom_theme <- theme_minimal() + 
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(vjust=5),
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        # axis.ticks = element_line(),
        legend.position = "none"
  )
theme_set(custom_theme)

colorbrewer2 <- rev(c(
  "#f7fcf0",
  "#e0f3db",
  "#ccebc5",
  "#a8ddb5",
  "#7bccc4",
  "#4eb3d3",
  "#2b8cbe",
  "#0868ac",
  "#084081"))


colorbrewer2_warm <- rev(c(
  "#ffffb2",
  "#fecc5c",
  "#fd8d3c",
  "#e31a1c"
))

names(colorbrewer2) <- 1:length(colorbrewer2)


# https://stackoverflow.com/questions/10504724/change-the-default-colour-palette-in-ggplot
# scale_aesthetic_discrete <- function(...) scale_fill_manual(values = colorbrewer2)
scale_fill_discrete <- function(...) scale_fill_manual(values = colorbrewer2)

# to our great dismay scale_color_* doesn't work
scale_colour_discrete <- function(...) scale_colour_manual(values = colorbrewer2_warm)
```


# More notes on how to do things


## The chain example in the paper

P(cyl, gear|am)

```{r}
prodplot(mtcars, ~ cyl + gear | am,  c("vspine", "vspine", "hbar")) + aes(fill=cyl, color = gear)
# ggsave("../figures/chain_cyl_gear_am.pdf", width = 2, height = 2)
```


The version that looks more like a tree map

```{r}
prodplot(mtcars, ~ cyl + gear + am,  c("hspine", "vspine", "hbar")) + aes(fill=cyl, color = gear)
# ggsave("../figures/chain_3var_tree.pdf", width = 3, height = 3)

```


The nice thing about `geom_density` is that there is no way to pick a bandwidth automatically and apply the same bandwidth to all groups/conditionals


```{r}
common_bw <- 1.5

p_correct <- ggplot(mtcars) + 
  geom_bloc(aes(
    x = c(mpg), 
    height = c(P(cyl|mpg), P(mpg)), 
    fill = factor(cyl)), bw = common_bw) +
  xlab("mpg")

p_incorrect <- 
  ggplot(mtcars) + 
  geom_density(aes(
    x = mpg,
    y = stat(density),
    fill = factor(cyl),
    color = factor(cyl)), # bw = 2.4 fixes this
    position = "stack", bw = common_bw) +
  xlab("mpg")

p_half_correct <- 
  ggplot(mtcars) + 
  geom_density(aes(
    x = mpg,
    y = stat(density * n),
    fill = factor(cyl),
    color = factor(cyl)), # bw = 2.4 fixes this
    position = "stack", bw = common_bw) 

p <- ggplot(mtcars) +  
  geom_bloc(aes(x = c(mpg), height = c(P(mpg))), bw = common_bw) +
  xlab("mpg")

alles<-grid.arrange(p,p_incorrect, p_correct, nrow = 1)
alles
# scaling <- 1.5
# ggsave("../figures/density_new_raw.pdf", plot = alles, width = 4.6 * scaling, height = 1.3 * scaling)
```


#### reasoning mistake

```{r}
mtcars %>%
  ggplot(aes(x = mpg, y=stat(density), fill = factor(cyl), color = NA, alpha = 0.5)) + 
    geom_density(bw = common_bw)

#ggsave("../figures/density_separate_raw.pdf", width = 7, height = 4)


```

Violating the The Principle of Visual-Data Correspondence:

if we remove _half_ of the 8-cylinder cars ($D \rightarrow D$), the plot looks almost the same --- the region for 8-cylinder in fact remains to be 1/3 of the total density area.

```{r}
subset_incorrect <- mtcars %>%
  group_by(cyl) %>%
  filter((cyl == 8) & row_number() %% 2 ==0 | cyl != 8) %>%
  ggplot(aes(x = mpg, y=stat(density), fill = factor(cyl), color = NA)) + 
  geom_density(bw = common_bw, position = "stack") + 
  labs(title = "Half of 8-cylinder data removed")

p_incorrect <- p_incorrect + labs(title = "All data")


subset_correct <- mtcars %>%
  group_by(cyl) %>%
  filter((cyl == 8) & row_number() %% 2 ==0 | cyl != 8) %>%
  ggplot() + 
 geom_bloc(aes(
    x = c(mpg), 
    height = c(P(cyl|mpg), P(mpg)), 
    fill = factor(cyl)), bw = common_bw) +
  xlab("mpg")
  

explanation <- grid.arrange(p_incorrect, subset_incorrect, p_correct, subset_correct, nrow = 2)

# ggsave("../figures/density_explanation.pdf",plot = explanation, width = 7, height = 4)

```

ACHTUNG: dotplot version colors the [15, 20) bin differntly ... where did they 6-cylinders go?

```{r}
ggplot(mtcars) + 
  geom_dotplot(aes(x =  cut_width(mpg,width = 5, boundary = 5), 
               fill = factor(cyl)), method = 'histodot', stackgroups = TRUE)
  
  ggplot(mtcars) + 
  geom_dotplot(aes(x =  cut_width(mpg,width = 5, boundary = 5), 
               fill = factor(cyl)), method = 'histodot', stackgroups = FALSE)
  
ggplot(mtcars, aes(x = mpg, fill = factor(cyl))) +
  geom_dotplot(method="histodot", binwidth = 5, stackgroups = TRUE)

ggplot(mtcars, aes(x = mpg, fill = factor(cyl))) +
  geom_dotplot(method="histodot", binwidth = 5, stackgroups = FALSE)
```



```{r}
ggplot(mtcars) + geom_density(aes(x =hp))
```




# pew example

```{r}
ggplot(mtcars) + 
  geom_bloc(aes(y = c(cyl), x = c(am), width = c(P(cyl|am))))
```



## Using base ggplot

Assuming x = am = race
y = cyl = generation

```{r}
mtcars %>%
  group_by(cyl,am) %>%
  summarize(count.cyl = n()) %>%
  mutate( prop.cyl = count.cyl/sum(count.cyl)) %>%
  ggplot(aes(x = factor(cyl), y = prop.cyl)) + 
  geom_col() + 
  coord_flip() +
  facet_grid(.~am)
```






# Pie chart analogy


```{r}
# Nope not this one
ggplot(mtcars) +
  geom_bar(aes(x = factor(cyl), fill = factor(cyl))) + 
  coord_polar()
```



```{r}
mtcars %>%
  group_by(cyl) %>%
  summarize(count = n()) %>%
  ggplot() +
  geom_bar(aes(x = "", y = count, fill = factor(cyl)), stat = "identity") +
  coord_polar("y", start = 0) + 
  theme_void()
  
# ggsave("../figures/mtcar_pie.pdf", width = 4, height = 3)
```
