---
title: "Examples"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: inline
---

editor_options:
  chunk_output_type: console
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
library(uncertainty.gogr)
```


# Override default themes

```{r}
custom_theme <- theme_minimal() + 
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(vjust=5),
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        # axis.ticks = element_line(),
        legend.position = "none"
  )
theme_set(custom_theme)

colorbrewer2 <- rev(c(
  "#f7fcf0",
  "#e0f3db",
  "#ccebc5",
  "#a8ddb5",
  "#7bccc4",
  "#4eb3d3",
  "#2b8cbe",
  "#0868ac",
  "#084081"))


colorbrewer2_warm <- rev(c(
  "#ffffb2",
  "#fecc5c",
  "#fd8d3c",
  "#e31a1c"
))

names(colorbrewer2) <- 1:length(colorbrewer2)


# https://stackoverflow.com/questions/10504724/change-the-default-colour-palette-in-ggplot
# scale_aesthetic_discrete <- function(...) scale_fill_manual(values = colorbrewer2)
scale_fill_discrete <- function(...) scale_fill_manual(values = colorbrewer2)

# to our great dismay scale_color_* doesn't work
scale_colour_discrete <- function(...) scale_colour_manual(values = colorbrewer2_warm)
```


# geom_bloc

Assuming B,C, etc. are discrete variables

## Product/area plots for discrete A

### {w,h} <- P(A)

```{r}
ggplot(mtcars) + geom_bloc(aes(width = c(P(cyl)))) 
```

### {w,h} <- P(A), {x,y} <- A

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl)), x = c(cyl)))
```

TODO: new combination 

  w <- P(A)
  x <-A

### {w,h} <- P(A|B), {x,y} <- (A),B

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl|gear)), x = c(gear)))
```


```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl|gear)), x = c(cyl), y = c(gear)))

```



### {w,h} <- P(A|B,C), {x,y} <- B,C

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl|gear, carb)), x = c(gear), y=c(carb)))
```

### 1+ probabilistic variables

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(gear|am), P(cyl|gear, am)), 
                               x = c(am)))

ggplot(mtcars) + geom_bloc(aes(height = c(P(gear|am)), 
                               width = c(P(cyl|gear, am)), 
                               y = c(am)))

ggplot(mtcars) + geom_bloc(aes(height = c(P(gear), P(cyl|gear))))

ggplot(mtcars) + geom_bloc(aes(height = c(P(gear|am), P(cyl|gear, am)), 
                               x = c(gear), 
                               y = c(am)))
```


## Density plots for continuous A


### h <- P(A), x <- A

  x <- A
  height <- P(A)

```{r}
ggplot(mtcars) +  geom_bloc(aes(x = c(mpg), height = c(P(mpg)))) 
```

### h <- P(A|B), x <- A, f <- B

`fill = cyl` cannot be omitted

```{r}
ggplot(mtcars) + geom_bloc(aes(x = mpg, fill = cyl, height = c(P(mpg | cyl))))
```


### h <- P(A|B), x <- A, y <- B
  
Ridge plots
  
```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg), height = c(P(mpg | cyl)), y = c(cyl), fill = cyl))
```

### h <- P(A|B,C), x <- A, y <- B, f <- C

More conditionals

```{r}
ggplot(mtcars) + geom_bloc(
  aes(
    x = c(mpg),
    y = c(gear), 
    fill = factor(cyl),
    height = c(P(mpg | gear, cyl))
  ))
```


Issue #58 TODO/bug: this should be different from above; should be faceting?

```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg,cyl), y = c(gear), fill=factor(cyl), height = c(P(mpg | gear, cyl))))
```

### h <- P(B|A), x <- A, f <- B

TODO/bug: position needs to be "fill" in `geom_bloc`

```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg), 
                               height = c(P(cyl | mpg)), 
                               fill = factor(cyl)), 
                           position = "fill") # need fixing
```

```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg, gear), height = c(P(cyl | gear,mpg))))
```


### P(B,A,...)

```{r}
common_bw <- 1.5


ggplot(mtcars) + 
  geom_bloc(aes(
    x = c(mpg), 
    height = c(P(cyl|mpg), P(mpg)), 
    fill = factor(cyl)), bw = common_bw) +
  xlab("mpg")
```



```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(hp, gear), fill = factor(cyl), height = c(P(cyl|hp, gear), P(hp|gear))))
```

TODO: more conds

# geom_icon

Using `geom_bloc` first to get the base partition right

```{r}
ggplot(mtcars) + geom_icon(aes(height = c(P(cyl|gear)), x = c(gear), fill = c(factor(cyl))), stat = "icon") +
  scale_fill_brewer(palette = "Accent") +
  theme_minimal() 
```

```{r}
ggplot(mtcars) + geom_icon(aes(height = c(P(cyl|gear), P(gear)), x = c(gear, vs)), stat = "icon") +
  coord_fixed()
```

```{r}
ggplot(mtcars) + geom_icon(aes(height = c(P(cyl|carb)), y=c(carb)), stat = "icon") +
  # scale_fill_brewer(palette = "Accent") + 
  # theme_minimal() + 
  NULL
```


```{r}
ggplot(mtcars) + 
  geom_icon(aes(height = c(P(cyl|gear, vs)), x = c(gear), y=c(vs))) +
  # geom_bloc(aes(height = c(P(cyl|gear, vs)), x = c(gear), y=c(vs))) + 
  coord_fixed()
```


## vspine

```{r}
ggplot(mtcars) + 
  geom_icon(aes(height = c(P(cyl)))) + 
  # geom_bloc(aes(height = c(P(cyl)))) + 
  coord_fixed()
```

## hspine

```{r}
ggplot(mtcars) + 
  geom_icon(aes(width = c(P(cyl)))) + 
  geom_bloc(aes(width = c(P(cyl)))) + 
  coord_fixed()
```

## dotplots

```{r}
ggplot(mtcars) + 
  geom_icon(aes(height = c(P(cyl))))
```




