---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
editor_options:
  chunk_output_type: console
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
```

```{r}

custom_theme <- theme_minimal() + 
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank(),
        axis.ticks = element_line()
  )
theme_set(custom_theme)

colorbrewer2 <- rev(c(
  "#f7fcf0",
  "#e0f3db",
  "#ccebc5",
  "#a8ddb5",
  "#7bccc4",
  "#4eb3d3",
  "#2b8cbe",
  "#0868ac",
  "#084081"))

names(colorbrewer2) <- 1:length(colorbrewer2)


# https://stackoverflow.com/questions/10504724/change-the-default-colour-palette-in-ggplot
scale_aesthetic_discrete <- function(...) scale_fill_manual(values = colorbrewer2)

# to our great dismay scale_color_* doesn't work
scale_colour_discrete <- function(...) scale_colour_manual(values = colorbrewer2)
```


# geom_bloc

## product plots

```{r}
ggplot(mtcars) + geom_bloc(aes(width = c(P(cyl))))
```

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl|gear)), x = c(gear)))
```

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl)), x = c(cyl)))
```

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl|gear, carb)), x = c(gear, carb)))
```

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl|gear, carb)), x = c(gear), y=c(carb)))
```

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(gear|am), P(cyl|gear, am)), x = c(gear), y = c(am)))
```


## density plots


### P(A|...)

  x <- A
  height <- P(A)

```{r}
ggplot(mtcars) +  geom_bloc(aes(x = c(mpg), height = c(P(mpg)))) 
```

P(A|B)

TODO: this spec is wrong

```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg, cyl), height = c(P(mpg | cyl)), colour = factor(cyl)))
```

  x <- A
  color <- B
  height <- P(A|B)

```{r}
ggplot(mtcars) + geom_bloc(aes(
    x = c(mpg), 
   height = c(P(mpg | cyl)), 
   fill = factor(cyl)))  + 
  scale_fill_brewer(palette = "Accent") + theme_minimal()

```


Ridge plots
  
  x <- A
  y <- B
  height <- P(A|B)

```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg), height = c(P(mpg | cyl)), y = c(cyl)))
```

  x <- A
  y <- B
  color <- B
  height <- P(A|B)

```{r}
ggplot(mtcars) + geom_bloc(aes(
  x = c(mpg), 
  y = c(cyl),
  height = c(P(mpg | cyl)),  
  color = factor(cyl)
))
```




more conds

```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg,gear), y = c(cyl), height = c(P(mpg | gear, cyl))))
```

### P(B|A, ...)

TODO: position needs to be "fill"

```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg), height = c(P(cyl | mpg)), fill = factor(cyl)))
```

```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg, gear), height = c(P(cyl | gear,mpg))))
```


### P(B,A,...)

The nice thing about `geom_density` is that there is no way to pick a bandwidth automatically and apply the same bandwidth to all groups/conditionals


```{r}
p_correct <- ggplot(mtcars) + 
    geom_bloc(aes(
    x = c(mpg), 
    height = c(P(cyl|mpg), P(mpg)), 
    fill = factor(cyl)) # bw = 10, etc
    )

p_half_correct <- 
  ggplot(mtcars) + 
  geom_density(aes(
    x = mpg,
    y = stat(density * n),
    fill = factor(cyl),
    color = factor(cyl)), # bw = 2.4 fixes this
    position = "stack") 

p <- ggplot(mtcars) +  geom_bloc(aes(x = c(mpg), height = c(P(mpg))))

grid.arrange(p, p_half_correct, p_correct, nrow = 1)
```

```{r}
ggplot(mtcars) + geom_density(aes(x =hp))
```


```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(hp, gear), fill = factor(cyl), height = c(P(cyl|hp, gear), P(hp|gear))))
```

TODO: more conds

# geom_icon

Using `geom_bloc` first to get the base partition right

```{r}
ggplot(mtcars) + geom_icon(aes(height = c(P(cyl|gear)), x = c(gear), fill = c(factor(cyl))), stat = "icon") +
  scale_fill_brewer(palette = "Accent") +
  theme_minimal() 
```

```{r}
ggplot(mtcars) + geom_icon(aes(height = c(P(cyl|gear), P(gear)), x = c(gear, vs)), stat = "icon") +
  coord_fixed()
```

```{r}
ggplot(mtcars) + geom_icon(aes(height = c(P(cyl|carb)), y=c(carb)), stat = "icon") +
  # scale_fill_brewer(palette = "Accent") + 
  # theme_minimal() + 
  NULL
```


```{r}
ggplot(mtcars) + 
  geom_icon(aes(height = c(P(cyl|gear, vs)), x = c(gear), y=c(vs))) +
  # geom_bloc(aes(height = c(P(cyl|gear, vs)), x = c(gear), y=c(vs))) + 
  coord_fixed()
```


## vspine

```{r}
ggplot(mtcars) + 
  geom_icon(aes(height = c(P(cyl)))) + 
  # geom_bloc(aes(height = c(P(cyl)))) + 
  coord_fixed()
```

## hspine

```{r}
ggplot(mtcars) + 
  geom_icon(aes(width = c(P(cyl)))) + 
  geom_bloc(aes(width = c(P(cyl)))) + 
  coord_fixed()
```

## dotplots

```{r}
ggplot(mtcars) + 
  geom_icon(aes(height = c(P(cyl))))
```


# pew example

```{r}
ggplot(mtcars) + 
  geom_bloc(aes(y = c(cyl), x = c(am), width = c(P(cyl|am))))
```

