---
title: "Examples"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: inline
---

editor_options:
  chunk_output_type: console
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
library(gridExtra)
library(ggplot2)
library(pgog)
```



# Override default themes

```{r}
custom_theme <- theme_minimal() + 
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(vjust=5),
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        # axis.ticks = element_line(),
        legend.position = "none"
  )
theme_set(custom_theme)

colorbrewer2 <- rev(c(
  "#f7fcf0",
  "#e0f3db",
  "#ccebc5",
  "#a8ddb5",
  "#7bccc4",
  "#4eb3d3",
  "#2b8cbe",
  "#0868ac",
  "#084081"))


colorbrewer2_warm <- rev(c(
  "#ffffb2",
  "#fecc5c",
  "#fd8d3c",
  "#e31a1c"
))

names(colorbrewer2) <- 1:length(colorbrewer2)


# https://stackoverflow.com/questions/10504724/change-the-default-colour-palette-in-ggplot
# scale_aesthetic_discrete <- function(...) scale_fill_manual(values = colorbrewer2)
scale_fill_discrete <- function(...) scale_fill_manual(values = colorbrewer2)

# to our great dismay scale_color_* doesn't work
scale_colour_discrete <- function(...) scale_colour_manual(values = colorbrewer2_warm)
```


# geom_bloc

Assuming B,C, etc. are discrete variables

## Product/area plots for discrete A

### {w,h} <- P(A)

```{r}
ggplot(mtcars) + geom_bloc(aes(width = c(P(cyl),fill = factor(cyl))))
```

### {w,h} <- P(A), {x,y} <- A

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl)), x = c(cyl)))
```

TODO: new combination 

  w <- P(A)
  x <-A

### {w,h} <- P(A|B), {x,y} <- (A),B

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl|gear)), x = c(gear), fill = factor(gear)))
```


```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl|gear)), x = c(cyl), y = c(gear)))

```



### {w,h} <- P(A|B,C), {x,y} <- B,C

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(cyl|gear, carb)), x = c(gear), y=c(carb)))
```

### 1+ probabilistic variables

```{r}
ggplot(mtcars) + geom_bloc(aes(height = c(P(gear|am), P(cyl|gear, am)), 
                               x = c(am)))

ggplot(mtcars) + geom_bloc(aes(height = c(P(gear|am)), 
                               width = c(P(cyl|gear, am)), 
                               y = c(am)))

ggplot(mtcars) + geom_bloc(aes(height = c(P(gear), P(cyl|gear))))

ggplot(mtcars) + geom_bloc(aes(height = c(P(gear|am), P(cyl|gear, am)), 
                               x = c(gear), 
                               y = c(am)))
```


## Density plots for continuous A

Currently PGoG only includes `x, height` or `y, width` combinations for density plots. All of the examples in this subsection should work `y, width` as well. 


### {w,h} <- P(A)

Doesn't exist yet in the grammar. 

### h <- P(A), x <- A


```{r}
ggplot(mtcars) +  geom_bloc(aes(x = c(mpg), height = c(P(mpg)))) 
```


Alternatively, w <- P(A), y <- A

TODO: this is not rotated hmmm issue #59

```{r}
ggplot(mtcars) +  geom_bloc(aes(y = c(mpg), width = c(P(mpg)))) 
```


### h <- P(A|B), x <- A, f <- B

`fill = cyl` cannot be omitted

```{r}
ggplot(mtcars) + geom_bloc(aes(x = mpg, fill = cyl, height = c(P(mpg | cyl))))
```


### h <- P(A|B), x <- A, y <- B
  
Ridge plots
  
```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg), height = c(P(mpg | cyl)), y = c(cyl), fill = cyl))
```

### h <- P(A|B,C), x <- A, y <- B, f <- C

More conditionals

```{r}
ggplot(mtcars) + geom_bloc(
  aes(
    x = c(mpg),
    y = c(gear), 
    fill = factor(cyl),
    height = c(P(mpg | gear, cyl))
  ))
```


Issue #58 TODO/bug: this should be different from above; should be faceting?

```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg,cyl), y = c(gear), fill=factor(cyl), height = c(P(mpg | gear, cyl))))
```

### h <- P(B|A), x <- A, f <- B

TODO/bug: position needs to be "fill" in `geom_bloc`

```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg), 
                               height = c(P(cyl | mpg)), 
                               fill = factor(cyl)), 
                           position = "fill") # need fixing
```

Issue #58 TODO/bug

```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(mpg, gear), height = c(P(cyl | gear,mpg))))
```


### 1+ probabilistic variables

More than one probabilistic variables in the spec

```{r}
common_bw <- 1.5

ggplot(mtcars) + 
  geom_bloc(aes(
    x = c(mpg), 
    height = c(P(cyl|mpg), P(mpg)), 
    fill = factor(cyl)), bw = common_bw, position = "stack") + # TODO: remove position arg
  xlab("mpg")
```



```{r}
ggplot(mtcars) + geom_bloc(aes(x = c(hp, gear), fill = factor(cyl), height = c(P(cyl|hp, gear), P(hp|gear))), position = "stack")
```


# geom_icon

## Discrete var (icon arrays)

### {w,h} <- P(A)

aka spine plots

```{r}
ggplot(mtcars) + geom_icon(aes(height=c(P(cyl))))
```

```{r}
ggplot(mtcars) + geom_icon(aes(width=c(P(cyl))))
```

TODO: can't add fill color Computation failed in `stat_icon()`: could not find function "divider"

https://github.com/MUCollective/pgog/issues/60

```{r}
# ggplot(mtcars) + geom_icon(aes(height=c(P(cyl)), fill= cyl))
```

### {w,h} <- P(A), x,y <- A

bar charts filled with icons 

```{r}
ggplot(mtcars) + geom_icon(aes(
  height = c(P(cyl)), 
  x = c(cyl), 
  fill = c(factor(cyl)
  ))) 
```

This is just ugly
|
V

```{r}
ggplot(mtcars) + geom_icon(aes(
  width = c(P(cyl)), 
  y = c(cyl), 
  fill = c(factor(cyl)
  ))) 
```


### {w,h} <- P(A|B), {x,y} <- (A),B

```{r}
ggplot(mtcars) + geom_icon(aes(height = c(P(cyl|gear)), x = c(gear)))
```

TODO: this one is supposed to be different from the prev one?

```{r}
ggplot(mtcars) + geom_icon(aes(height = c(P(cyl|gear)), x = c(cyl, gear)))
```



TODO: these spec are wrong why does the parser not catch it

```{r}
# ggplot(mtcars) + geom_icon(aes(height = c(P(gear)), x = c(gear, cyl)))

# ggplot(mtcars) + geom_icon(aes(height = c(P(cyl|gear), P(gear)), x = c(gear, vs)))
```


### {w,h} <- P(A|B,C), {x,y} <- B,C

```{r}
ggplot(mtcars) + 
  geom_icon(aes(height = c(P(cyl|gear, vs)), x = c(gear), y=c(vs))) 
```



## Continuous var (dotplots)

TODO: need implementing

### {w,h} <- P(A)


```{r}
# ggplot(mtcars) + geom_icon(aes(height=c(P(mpg))))
```

## x.width and y.height
```{r}
ggplot(mtcars) + geom_bloc(aes(width = c(P(cyl)), x = c(cyl)))
```
```{r}
# ggplot(mtcars) + geom_icon(aes(width=c(P(mpg))))
```


### {w,h} <- P(A), x,y <- A


### {w,h} <- P(A|B), {x,y} <- (A),B
### {w,h} <- P(A|B,C), {x,y} <- B,C



```{r}
df_test_1 = data.frame(generation = c("Post-Millennials in 2018"), 
                       race = c(rep("White",52),rep("Hispanic",25),rep("Black",14),rep("Asian",6),rep("Other",4)))
df_test_2 = data.frame(generation = c("Millennials in 2002"), 
                       race = c(rep("White",61),rep("Hispanic",18),rep("Black",15),rep("Asian",4),rep("Other",1)))
df_test_3 = data.frame(generation = c("Gen-Xer in 1986"), 
                       race = c(rep("White",70),rep("Hispanic",12),rep("Black",15),rep("Other",3)))
df_test_4 = data.frame(generation = c("Early Boomers in 1986"), 
                       race = c(rep("White",82),rep("Hispanic",4),rep("Black",13),rep("Asian",1),rep("Other",1)))

df_total = rbind(df_test_1,df_test_2,df_test_3,df_test_4)
df_total = df_total %>% mutate(generation = fct_relevel(generation, "Early Boomers in 1986","Gen-Xer in 1986","Millennials in 2002", "Post-Millennials in 2018"), race = fct_relevel(race, "White", "Hispanic", "Black", "Asian", "Other"))

ggplot(df_total) + geom_bloc(aes(width = c(P(race|generation)), x = c(race), y = c(generation),fill = generation), fill = "black") + theme_bw()
```


