---
title: "Representations of probabilistic data"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(devtools)
library(riskyr)
library(rv2)
library(tidyverse)
library(ggplot2)
library(ggridges)
library(scales)
```

# Example dataset

For this made-up dataset: `prev = .1, sens = .70, spec =   NA, fart = .090, N = 100`, create a dataframe instead of having four function arguments

- Pro: an handle more than two variables, not limited to binary variables, like tidy data?
- Con: inefficient?

Spec: 

- Each row is one sample
- Each column is a random variable
- Each cell is a number (or factor)???





## As dataframe

### Each row is a sample

Like tidy format?

```{r}
data(cancer)
str(cancer)
```


### TODO: Column list

```{r}
cancer %>%
  nest(-test)
```


## As random variable


TODO: How to express conditional probabilities?

```{r}
cancer_rv <- rv(x = c(1, 0), probs = c(0.1, 0.9))
test_rv <- rv(x = c(1,0), probs = c(0.15, 0.85))
```






# Other packages

## riskyr

Generating frequencies from probabilities

```{r}
f1 <- comp_freq_prob(prev = .1, sens = .70, spec =   NA, fart = .090, N = 100)
length(f1)
str(f1)
```


## rv2

- Random variable
- simulate from prob. distributions

```{r}
dice <- rv(1:6)
dice
plot(dice)
P(dice <= 3)
E(dice) 
rsim(dice, 100) # simulate random numbers from rv
```



